---
title: "Activity 6 - Logistic Regression"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r load_packages}
library(tidyverse)
library(tidymodels)
library(ggplot2)
```

## Loading Data
Link to data: [Resume](https://www.openintro.org/data/csv/resume.csv)

```{r}
resume = read.csv("https://www.openintro.org/data/csv/resume.csv")
resume

```
1.  Is this an observational study or an experiment? Explain. 
__Experimental study because, the researchers focus on establishing the couse and effect relationship between dependent and independent variables.__

2.  The variable of interest is `received_callback`. What type of
    variable is this? What do the values represent? 
    __Categorical variable, the values represent whether candidates were called after their resumes were received or not.__

3.  For `received_callback`, create an appropriate data visualization
    using `{ggplot2}`. Be sure to provide more descriptive labels (both
    axes labels and value labels - there are many ways to do this) as
    well as an appropriate title.
```{r received_callback_viz}
ggplot(resume, aes(x = received_callback)) +
  geom_bar() +
  labs(x = "Received Callback", y = "Count of callbacks") +
  scale_x_discrete(labels = c("No", "Yes"), breaks = c(0, 1))
```
    
    
    

4.  Below, I provide you with a numerical summary table that should
    reiterate (i.e., provides numerical values) your plot in (3). Write
    the code to produce this table.

| received_callback |    n | percent |
|:------------------|-----:|--------:|
| No                | 4478 |   91.95 |
| Yes               |  392 |    8.05 |


```{r group_data}
grouped_data <- resume %>%
  group_by(received_callback = ifelse(received_callback == 1, "Yes", "No")) %>%
  summarise(count = n()) %>%
  mutate(percent = round(count / sum(count) * 100, 2))

grouped_data
```

5.  Using the output from (4) and (5), what do you notice?
__The number call backs not received is significantly higher than received call backs__

Using your output from (4) and (5), answer the following questions:

6.  What is the probability that a randomly selected résumé/person will
    be called back? Approximately 8%

7.  What are the [**odds**](https://en.wikipedia.org/wiki/Odds) that a
    randomly selected résumé/person will be called back?
    __8% or 0.8__
    
| received_callback | Black        | White        |
|:------------------|:-------------|:-------------|
| No                | 93.55 (2278) | 90.35 (2200) |
| Yes               | 6.45 (157)   | 9.65 (235)   |

Using the above table, answer the following question:

6.  What is the probability that a randomly selected résumé/person
    perceived as Black will be called back?
    __~6%__

7.  What are the **odds** that a randomly selected résumé/person
    perceived as Black will be called back?
    __~6%__
    
    
```{r model}
# The {tidymodels} method for logistic regression requires that the response be a factor variable
resume <- resume %>% 
  mutate(received_callback = as.factor(received_callback))

resume_mod <- logistic_reg() %>%
  set_engine("glm") %>%
  fit(received_callback ~ race, data = resume, family = "binomial")

tidy(resume_mod) %>% 
  knitr::kable(digits = 3)
```
    
```{r}
resume_select <- resume %>% 
  rename(sex = gender) %>% 
  filter(job_city == "Chicago") %>% 
  mutate(race = case_when(
         race == "white" ~ "White",
         TRUE ~ "Black"
       ),
       sex = case_when(
         sex == "f" ~ "female",
         TRUE ~ "male"
       )) %>% 
  select(received_callback, years_experience, race, sex)
resume_select
```
    

```{r}
mult_log_mod <- glm(received_callback ~ years_experience + race + sex, data = resume_select, family = "binomial")

tidy(mult_log_mod)
```

```{r}
tidy(mult_log_mod, exponentiate = TRUE) %>% 
  knitr::kable(digits = 3)
```
```{r}
# To store residuals and create row number variable
mult_log_aug <- augment(mult_log_mod, type.predict = "response", 
                      type.residuals = "deviance") %>% 
                      mutate(id = row_number())

# Plot residuals vs fitted values
ggplot(data = mult_log_aug, aes(x = .fitted, y = .resid)) + 
geom_point() + 
geom_hline(yintercept = 0, color = "red") + 
labs(x = "Fitted values", 
     y = "Deviance residuals", 
     title = "Deviance residuals vs. fitted")

# Plot residuals vs row number
ggplot(data = mult_log_aug, aes(x = id, y = .resid)) + 
geom_point() + 
geom_hline(yintercept = 0, color = "red") + 
labs(x = "id", 
     y = "Deviance residuals", 
     title = "Deviance residuals vs. id")
```


